---
title: "Hello R"
author: "Alejandro Rodriguez"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 6
    fig_height: 6
    highlight: kate
    theme: flatly
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages


```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

**The data frame has 1846 rows and 3 columns** 

**The variables are 'dataset', 'x' and 'y'**

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
 filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
 geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3


```{r plot-star}
star_data = datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```
**The correlation in the star data is the same as the dino data**

### Exercise 4

```{r}
circle_data = datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r}
circle_data %>%
  summarize(r = cor(x, y))

```
**The correlation in the circle data is nearly the same as the correlation in the dino data**

### Exercise 5

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
 geom_point()+
 facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
 theme(legend.position = "none")
```

```{r}
datasaurus_dozen %>%
 group_by(dataset) %>%
 summarize(r = cor(x, y))
```

